Algomusicology, ????, Profit

### 2016-05-22 paper.tex
Fix double quotes.

David Meredith has used Kolmogorov complexity to compare the quality of musical analyses\cite{Analysis by Compression}.
He starts by assuming that musical analysis aims to produce "best possible explanation for musical works". If that's the case,
how might we compare two different analyses of the same piece?

@@

Using this idea, we can show that composing "Row, row, row your boat" out of sequences of durations and pitches
is a better description of the piece than the raw notes. \verb|;| indicates a comment in Clojure.

@@

The particularly significant compression in this way of writing "Row, row, row your boat" is the line \verb|(canon (simple 4))|.
A canon is when an initial melody (often known as the dux) is accompanied by a transformation of itself (often known as the comes).
In "Row, row, row your boat", the comes is a copy of the dux that is delayed by four beats, a structure known as a simple canon.

@@

Some books exhibit apparent sense, most exhibit none. The narrator describes one that is "a mere labyrinth of letters,
but the next-to-last page says \textit|Oh time thy pyramids|."

@@

Borges appreciated this paradox. His anonymous narrator reports that on "some shelf in some hexagon (men reasoned)
there must exist a book which is the formula and perfect compendium of all the rest". In other words, that one book
epitomises the complexity of the entire library, though it is part of the library.

@@

It is easily seen to be a lexicon for the decimal digits, because:
\begin{enumerate}
    \item By definition, the Champernowne word includes every natural number.
    \item Every sequence of digits corresponds to a natural number.
    \item Therefore, the Champernowne word contains all possible sequences of digits.
\end{enumerate}
Of course, a sequence of digits may occur earlier than its natural number - the sequence "34" first occurs when numbers three and
four are encountered, well in advance of the natural number 34.

@@

The Criminal Justice and Public Order Act 1994 was an attempt by the UK Government to curb rave culture. The musicological
dilemma encountered by the government of the day was how to define raves. They settled on prohibiting gatherings where
"a succession of repetitive beats" were played\cite{Joseph Gallivan on pop}.

The duo Autechre responded with the Anti EP\cite{Anti EP}, whose third track `Flutter', was designed to protest the legislation.
Band member
Sean Booth explained that they "made as many different bars as we could on the drum machine, then strung them all together."
\cite{Joseph Gallivan on pop}
In other words, as every bar features a unique beat, `Flutter' does not match the government's algomusicological description
of "repetitive beats".

Autechre appreciated the practical difficulties of negotiating the subtleties of complexity theory at 3am in a noisy field,
so they advised DJs to "have a lawyer and a musicologist present at all times to confirm the non repetitive nature of the
music in the event of police harassment."\cite{Joseph Gallivan on pop}

>>>>

David Meredith has used Kolmogorov complexity to compare the quality of musical analyses\cite{Analysis by Compression}.
He starts by assuming that musical analysis aims to produce ``best possible explanation for musical works". If that's the case,
how might we compare two different analyses of the same piece?

@@

Using this idea, we can show that composing ``Row, row, row your boat" out of sequences of durations and pitches
is a better description of the piece than the raw notes. \verb|;| indicates a comment in Clojure.

@@

The particularly significant compression in this way of writing ``Row, row, row your boat" is the line \verb|(canon (simple 4))|.
A canon is when an initial melody (often known as the dux) is accompanied by a transformation of itself (often known as the comes).
In ``Row, row, row your boat", the comes is a copy of the dux that is delayed by four beats, a structure known as a simple canon.

@@

Some books exhibit apparent sense, most exhibit none. The narrator describes one that is ``a mere labyrinth of letters,
but the next-to-last page says \textit|Oh time thy pyramids|."

@@

Borges appreciated this paradox. His anonymous narrator reports that on ``some shelf in some hexagon (men reasoned)
there must exist a book which is the formula and perfect compendium of all the rest". In other words, that one book
epitomises the complexity of the entire library, though it is part of the library.

@@

It is easily seen to be a lexicon for the decimal digits, because:
\begin{enumerate}
    \item By definition, the Champernowne word includes every natural number.
    \item Every sequence of digits corresponds to a natural number.
    \item Therefore, the Champernowne word contains all possible sequences of digits.
\end{enumerate}
Of course, a sequence of digits may occur earlier than its natural number - the sequence ``34" first occurs when numbers three and
four are encountered, well in advance of the natural number 34.

@@

The Criminal Justice and Public Order Act 1994 was an attempt by the UK Government to curb rave culture. The musicological
dilemma encountered by the government of the day was how to define raves. They settled on prohibiting gatherings where
``a succession of repetitive beats" were played\cite{Joseph Gallivan on pop}.

The duo Autechre responded with the Anti EP\cite{Anti EP}, whose third track `Flutter', was designed to protest the legislation.
Band member
Sean Booth explained that they ``made as many different bars as we could on the drum machine, then strung them all together."
\cite{Joseph Gallivan on pop}
In other words, as every bar features a unique beat, `Flutter' does not match the government's algomusicological description
of ``repetitive beats".

Autechre appreciated the practical difficulties of negotiating the subtleties of complexity theory at 3am in a noisy field,
so they advised DJs to ``have a lawyer and a musicologist present at all times to confirm the non repetitive nature of the
music in the event of police harassment."\cite{Joseph Gallivan on pop}
